%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{John ``Jack'' Truskowski} % Your name
\address{1010 E Washington Ave, Madison WI, 53703} % Your address
\address{(203)837-6494 \\ jtruskow@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Wisconsin-Madison}, Madison WI \hfill {\em September 2017 - December 2019 (estimated)}
\\ M.S. Computer Science
\\ Department of Computer Sciences\\

{\bf Bowdoin College}, Brunswick ME \hfill {\em September 2013 - May 2017}
\\ B.A. Computer Science.\hfill { Cum Laude | }
Minor in Music \smallskip \\
\end{rSection}

%% \begin{rSection}{Carrier Objective}
%%  To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
%% \end{rSection}

%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}
{\bf Teaching Assistant}, University of Wisconsin-Madison \hfill {\em September 2017 - Present}
\\\texttt{CS200} (4 semesters) - Introduction to Computer Science, a 600+ student course at UW-Madison taught in Java. Responsibilities include: Teach weekly lab sections, design and implement homework assignments, creation of an automated grading tool to grade hundreds of students' participation scores, grade student projects, hold weekly office hours. \\
---\\
\texttt{CS300} (1 semester) - Programming II, taught in the summer on the campus of Epic Systems. Responsibilities include: Hold weekly office hours to help students on weekly programming assignments. Grading of exams. Creation of automated test suites to grade weekly programming assignments in Java. Proctor midterms and final exam.

{\bf Teaching Assistant}, Bowdoin College \hfill {\em September 2014 - May 2017}\\
Hold weekly office hours to assist students. Communicate regularly with professors to ensure students are receiving help and problem areas are addressed. Also employed as a grader and private tutor of problem sets and programming assignments for Data Structures, AI, and Introduction to Computer Science. \\

{\bf Cognitive Computing Intern}, IBM \hfill {\em Summer 2016} \\
Worked in a team to apply machine learning to derive insights from customer data\\

{\bf Summer Research Fellow}, Bowdoin College \hfill {\em Summer 2015 - Fall 2016}\\
Awarded a grant to design and implement an interactive music system in Max/MSP/Jitter. Backend written in C++.

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages \ & Java, Python, C++, C, Swift \\
Software \& Tools & Unix, Emacs, \LaTeX, MS Office \\
\end{tabular}
\end{rSection}

\begin{rSection}{Academic Awards}
\item Cum Laude, Bowdoin College
\item 3-year Sarah and James Bowdoin Scholar (Top 20\% GPA)
\item Awarded Kibbe Fellowship for summer research
\end{rSection}

%% \begin{rSection}{Non-Academic Interests}
%%   Passionate about fitness, video games, and Japanese cars from the 90s
%% \end{rSection}

\end{document}
